Handling String-Number Conversion in String Constraint Solving

### 2019-11-15 draft.tex
add an alternative way to describe correctness lemmas
Encode functions to formulate lemmas

Through the paper, we will use quantifier-free linear integer arithmetic formulas, and call them \emph{linear formulas} for short.   
Given a linear formula $\phi$, a set of variables $V$, and an \emph{interpretation} of $V$, i.e., a function $I:V\rightarrow \nat$, 
we denote by $I\models_V \phi$ that $I$ satisfies $\phi$ (which is defined in the standard manner), and call $I$ a \emph{model} of $\phi$ over $V$. \lh{Our use of indexing by $V$ in the text later is not very nice. Add this for clarity?: If $V$ contain additional variables not present in $\phi$, the these might be assigned arbitrary values by $I$. If $V$ is missing some of the variables of $\phi$, then it must be possible to complete $I$ with assignment of the missing variables into a satisfying assignment of $\phi$ (as in existential quantification).}
We use $\modelsof \phi$ to denote the set all models of $\phi$ over $V$. 
We drop the reference to $V$ and write just ``model of $\phi$'',  $\modelsof \phi$, and $\models$ when no confusion may arise. For a set of interpretations $S$, we use $S_\Sigma$ to denote the set of interpretations obtained from $S$ by projecting the domain to $\Sigma$.

@@

@@

@@

\begin{lemma}\label{lemma:eqcorrect} For all $w_1 \in \semof{A_{x_1}} \ldots w_m \in \semof{A_{x_m}}$, we have

	\begin{center}
		$\exists (I^1\cup\pim^1)\cup\ldots\cup (I^m\cup\pim^m)$ in $\semof {\syncfof A {A'}  \wedge \Psi_{rename}}_{V_{x_1} \cup\ldots\cup V_{x_m}  \cup \#V_{x_1} \cup\ldots\cup \#V_{x_m} }$ s.t. $w_1=\decode A_{x_1}(I^1\cup\pim^1),\ldots,w_m=\decode A_{x_m}(I^m\cup\pim^m)$\\
		iff\\
		$w_1\cdot w_2 \cdots w_n = w_{n+1}\cdot w_{n+2} \cdots w_m$ and\\
		$\forall i,j \in [1,m]: x_i=x_j \Longrightarrow w_i=w_j$.
	\end{center}
\end{lemma}

@@

\begin{lemma}\label{lemma:sticorrect_neg}
	$\semof {\Psi_n \wedge \parikhfof {A_x} \wedge (v_0 = 0)\wedge (n = -1) }_{V_x \cup \#V_x \cup \{n\}} = 
	\{(I\cup\pim \cup I_n) \mid  I_n(n)= -1 \wedge \decode {A_x}(I\cup\pim) \not\in [0,9]^+  \}$
\end{lemma}
In this case, $x$ does not encode a number. The lemma says  the models we add to $\Phi_O$ represents words in both $\semof{A_x}$ and $[0,9]^+$, which means not a number, and $n$ is $-1$.}

>>>>

Through the paper, we will use quantifier-free linear integer arithmetic formulas, and call them \emph{linear formulas} for short.   
Given a linear formula $\phi$, a set of variables $V$, and an \emph{interpretation} of $V$, i.e., a function $I:V\rightarrow \nat$, 
we denote by $I\models_V \phi$ that $I$ satisfies $\phi$ (which is defined in the standard manner), and call $I$ a \emph{model} of $\phi$ over $V$. \lh{Our use of indexing by $V$ in the text later is not very nice. Add this for clarity?: If $V$ contain additional variables not present in $\phi$, the these might be assigned arbitrary values by $I$. If $V$ is missing some of the variables of $\phi$, then it must be possible to complete $I$ with assignment of the missing variables into a satisfying assignment of $\phi$ (as in existential quantification).}
We use $\modelsof \phi$ to denote the set all models of $\phi$ over $V$. 
We drop the reference to $V$ and write just ``model of $\phi$'',  $\modelsof \phi$, and $\models$ when no confusion may arise. For a set of interpretations $S$, we use $S_\Sigma$ to denote the set of interpretations obtained from $S$ by projecting the domain to $\Sigma$.
\lh{or really have just an equivalence of semantics indexed by variables?}

@@

\newcommand{\encode}[1]{\mathit{encode}_{#1}}
\lh{What about to put this somewhere, it will simplify formulation of the correctness lemmas. Roughly, formulation need to be polished a and explained:}
Given a PFA $A$, and a language $L\subseteq \Sigma^*$, we define the set of $A$ encodings of $L\cap \semof A$ as
the set $\encode A (L) = \{(I\cup\pim) \mid \decode A (I\cup \pim) \in L \cap \semof{A}\}$.
%
A domain restriction $R$ for a string contraint $\phi$ over variables $X$ is a mapping that assigns to every variable $x\in X$ a PFA $R(x)$ such that for different variables $x,y \in X$, $R(x)$ and $R(y)$ have disjoint sets of variables. 
%
For an interpretation $I:X\rightarrow \Sigma^*$, we define its $R$-encoding as the set $\encode R(I) = \bigcup_{x\in X} \encode A(I(x))$, and we left this notation to sets of interpretation in the standard manner, i.e. $\encode R J = \bigcup_{I \in J}\encode R (I)$.
%
In the following section, we will discuss how, given a string contraint $\phi$ and a domain restriction $R$,
to build an arithmetic formula $\Psi$ such that $\semof\Psi_{V_R\cup\#V_R} = \encode R(\semof{\phi})$. 
Tha is, formula $\Psi$ will capture $R$-encodings of soltuions of $\phi$ under the domain restriction given by $R$.

@@

\lh{
\begin{lemma}
${\semof {\syncfof {A_x }{A'} \land \Psi_{char}} } _{V_x \cup \pvarsof{V_x}} = \encode {A_x}(L(A))$
\end{lemma}
}

@@

\begin{lemma}\label{lemma:eqcorrect} For all $w_1 \in \semof{A_{x_1}} \ldots w_m \in \semof{A_{x_m}}$ satisfying $\forall i,j \in [1,m]: x_i=x_j \Longrightarrow w_i=w_j$, we have

	\begin{center}
		$\exists (I^1\cup\pim^1)\cup\ldots\cup (I^m\cup\pim^m)$ in $\semof {\syncfof A {A'}  \wedge \Psi_{rename}}_{V_{x_1} \cup\ldots\cup V_{x_m}  \cup \#V_{x_1} \cup\ldots\cup \#V_{x_m} }$ s.t. $w_1=\decode A_{x_1}(I^1\cup\pim^1),\ldots,w_m=\decode A_{x_m}(I^m\cup\pim^m)$\\
		iff\\
		$w_1\cdot w_2 \cdots w_n = w_{n+1}\cdot w_{n+2} \cdots w_m$.
	\end{center}
\end{lemma}

\lh{Assume that we were working with a domain restriction $R:[x_i]_1^m\rightarrow \text{PFAs}$.
\begin{lemma}
$\semof {\syncfof A {A'}  \wedge \Psi_{rename}}_{V_{x_1} \cup\ldots\cup V_{x_m}  \cup \#V_{x_1} \cup\ldots\cup \#V_{x_m} } = \encode R (\semof{\phi_e})$.
\end{lemma}
Also, we could denote by $V_R$ the varsiables $V_{x_1} \cup\ldots\cup V_{x_m}$ (these are the variables used by the domain restriction), 
and use $\# V_R$, so the lemma becomes \\ 
$\semof {\syncfof A {A'}  \wedge \Psi_{rename}}_{V_R \cup \# V_R} = \encode R (\semof{\phi_e})$.

@@

\begin{lemma}\label{lemma:sticorrect_neg}
	$\semof {\Psi_n \wedge \parikhfof {A_x} \wedge (v_0 = 0)\wedge (n = -1) }_{V_x \cup \#V_x \cup \{n\}} = 
	\{(I\cup\pim \cup I_n) \mid  I_n(n)= -1 \wedge \decode {A_x}(I\cup\pim) \not\in [0,9]^+  \}$
\end{lemma}

In this case, $x$ does not encode a number. The lemma says  the models we add to $\Phi_O$ represents words in both $\semof{A_x}$ and $[0,9]^+$, which means not a number, and $n$ is $-1$.}

\lh{
\begin{lemma}
$
\semof {\Psi_n \wedge \Psi_{v_0}\wedge \parikhfof {A_x} }_{V_x \cup \#V_x \cup \{n\}} = \encode  R(\semof{\phi_s})
$
\end{lemma}
The $n$ must somehow be handled properly by $\encode  R(\phi_s)$, I did not have time to think about it yet.
}
